---
title: "Importing MTurk JSON data"
output: html_document
author: Sophie Bridgers
---

Birch and Bloom (2007) Replication Project Data Analysis
=============================
# Libraries

```{r, message=FALSE}
library(jsonlite)
library(plyr)
library(dplyr)
library(tidyr)
setwd("~/Documents/Research/Projects/Psych254Rep/Data")

```

# Read in all the JSON strings

```{r comment=NA}

read.file <- function(filename) {
  con <- file(filename, "r", blocking = TRUE)
  lines <- paste(readLines(con, warn = FALSE), collapse = "\n")
  close(con)
  lines
}

json.dir <- "results/"
json.filenames <- paste0(json.dir, list.files(json.dir))
json.strings <- Map(read.file, json.filenames)
```

# Convert JSON to a R data frame

Merge all the json strings together, as if they are in a big array, and convert it to an R data frame:

```{r comment=NA}
strip.rownames <- function(x) {
  rownames(x) <- NULL
  x
}

json.superstring <- paste("[",paste(json.strings, collapse = ","),"]")
assignments <- fromJSON( json.superstring )

#Below I create separate data frames for the trial data (participants' responses), the condition data (which condition each participant is in), the total time data (how long the entire experiment took for each participant), and subject information data (the optional demographic information)

#Participants responses
trial.data <- Map(function(id, subject.trial.data) { cbind(workerid = id, subject.trial.data) },
                  assignments$WorkerId,
                  assignments$answers$trials)

#Condition information
condition.data <- Map(function(id, condition) { cbind(workerid = id, cond=condition) },
                  assignments$WorkerId,
                  assignments$answers$condition)

#Length of experiment
total.time.data <- Map(function(id, total.time.data) { cbind(workerid = id, total_time=total.time.data) },
                  assignments$WorkerId,
                  assignments$answers$time_in_minutes)

#Subject/demographic information
sub.data <- cbind(workerid = assignments$WorkerId,
                  assignments$answers$subject_information)
   
trial.data <- strip.rownames(do.call(rbind, trial.data))
condition.data <- strip.rownames(do.call(rbind, condition.data))
total.time.data <- strip.rownames(do.call(rbind, total.time.data))

condition.data <- data.frame(condition.data)
total.time.data <- data.frame(total.time.data)

#Return the data frames created above
trial.data
condition.data
total.time.data
sub.data


```

Next I combine the trial data, condition data, and total time data into a tidy data frame (i.e., I clean the data).

``` {r join_data}

#Join trial.data, condition.data, and total.time.data into wide data frame (I also re-order and re-name the columns)

d.wide <- trial.data %>%
        left_join(condition.data, by = "workerid") %>%
        right_join(total.time.data, by = "workerid") %>%
        select(workerid, cond, response_blue, response_red, 
               response_purple, response_green, rt_in_seconds, total_time) %>%
        dplyr::rename(blue=response_blue,
               red=response_red,
               purple=response_purple,
               green=response_green,
               rt_sec=rt_in_seconds,
               totaltime_min=total_time)

#Convert d.wide to tidy data frame, d.tidy (i.e., long format)

d.tidy <- d.wide %>%
    gather(container, response, blue,red,purple,green)

#Convert response from character to numeric
d.tidy$response <- as.numeric(d.tidy$response)
```

#Basic Stats

Next, I compute the mean response for each container by condition.

``` {r stats}
#Functions to calculate standard error of the mean and 95% confidence intervals
sem <- function(x) {sd(x) / sqrt(length(x))}
ci95 <- function(x) {sem(x) * 1.96}

#Computes the mean participant response for each container by condition
d.stats <- d.tidy %>%
    ungroup() %>%
    group_by(cond, container) %>%
    dplyr::summarise(avg_resp = mean(response),
                     sterr = sem(response))

d.stats

```

