---
title: "Importing MTurk JSON data"
output: html_document
author: Sophie Bridgers
---

Birch and Bloom (2007) Replication Project Data Analysis
=============================
# Libraries

```{r, message=FALSE}
library(jsonlite)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
setwd("~/Documents/Research/Projects/Psych254Rep/Data")

```

# Read in all the JSON strings

```{r comment=NA}

read.file <- function(filename) {
  con <- file(filename, "r", blocking = TRUE)
  lines <- paste(readLines(con, warn = FALSE), collapse = "\n")
  close(con)
  lines
}

json.dir <- "results/"
json.filenames <- paste0(json.dir, list.files(json.dir))
json.strings <- Map(read.file, json.filenames)
```

# Convert JSON to a R data frame

Merge all the json strings together, as if they are in a big array, and convert it to an R data frame:

```{r comment=NA}
strip.rownames <- function(x) {
  rownames(x) <- NULL
  x
}

json.superstring <- paste("[",paste(json.strings, collapse = ","),"]")
assignments <- fromJSON( json.superstring )

#Below I create separate data frames for the trial data (participants' responses), the condition data (which condition each participant is in), the total time data (how long the entire experiment took for each participant), and subject information data (the optional demographic information)

#Participants responses
trial.data <- Map(function(id, subject.trial.data) { cbind(workerid = id, subject.trial.data) },
                  assignments$WorkerId,
                  assignments$answers$trials)

#Condition information
condition.data <- Map(function(id, condition) { cbind(workerid = id, cond=condition) },
                  assignments$WorkerId,
                  assignments$answers$condition)

#Length of experiment
total.time.data <- Map(function(id, total.time.data) { cbind(workerid = id, total_time=total.time.data) },
                  assignments$WorkerId,
                  assignments$answers$time_in_minutes)

#Subject/demographic information
sub.data <- cbind(workerid = assignments$WorkerId,
                  assignments$answers$subject_information)
sub.data$gender = as.factor(sub.data$gender)
   
trial.data <- strip.rownames(do.call(rbind, trial.data))
condition.data <- strip.rownames(do.call(rbind, condition.data))
total.time.data <- strip.rownames(do.call(rbind, total.time.data))

condition.data <- data.frame(condition.data)
total.time.data <- data.frame(total.time.data)


#Return the data frames created above
trial.data
condition.data
total.time.data
sub.data


```

Next I combine the trial data, condition data, and total time data into a tidy data frame (i.e., I clean the data).

``` {r join_data}

#Join trial.data, condition.data, and total.time.data into wide data frame (I also re-order and re-name the columns)

d.wide <- trial.data %>%
        left_join(condition.data, by = "workerid") %>%
        right_join(total.time.data, by = "workerid") %>%
        select(workerid, cond, response_blue, response_red, 
               response_purple, response_green, rt_in_seconds, total_time) %>%
        dplyr::rename(blue=response_blue,
               red=response_red,
               purple=response_purple,
               green=response_green,
               rt_sec=rt_in_seconds,
               totaltime_min=total_time)

#Convert responses from character to numeric
d.wide$red <- as.numeric(d.wide$red)
d.wide$blue <- as.numeric(d.wide$blue)
d.wide$green <- as.numeric(d.wide$green)
d.wide$purple <- as.numeric(d.wide$purple)

#Calculate sum of responses to each container
d.wide$response_sum <- d.wide$blue + d.wide$red + d.wide$purple + d.wide$green

#Normalize responses
d.wide$red_norm <- (d.wide$red / d.wide$response_sum)*100
d.wide$blue_norm <- (d.wide$blue / d.wide$response_sum)*100
d.wide$purple_norm <- (d.wide$purple / d.wide$response_sum)*100
d.wide$green_norm <- (d.wide$green / d.wide$response_sum)*100

#Convert d.wide to tidy data frame, d.tidy (i.e., long format)

d.tidy <- d.wide %>%
    gather(container, response_norm, blue_norm,red_norm,purple_norm,green_norm)

#Convert response from character to numeric
#d.tidy$response <- as.numeric(d.tidy$response)
```

#Basic Stats

Next, I compute the mean response for each container by condition.

``` {r stats}
#Functions to calculate standard error and 95% confidence intervals
sem <- function(x) {sd(x) / sqrt(length(x))}
ci95 <- function(x) {sem(x) * 1.96}

#Computes the mean participant response for each container by condition
d.stats <- d.tidy %>%
    ungroup() %>%
    group_by(cond, container) %>%
    dplyr::summarise(avg_resp = mean(response_norm),
                     sterr = sem(response_norm),
                     ci95 = ci95(response_norm))

d.stats
```

``` {r plotting data}

#Alternative graph
data_plot = ggplot(data = d.stats, 
                   aes(x = container, y = avg_resp, fill = container)) + 
  geom_bar(stat = "identity") + facet_wrap(~cond) +  
  geom_errorbar(width = .1, aes(ymin = avg_resp - ci95, ymax = avg_resp + ci95)) +
  scale_fill_manual(values=c("#0066CC", "#FF3333", "#990099", "#669933"),
                      labels=c("Blue", "Red", "Purple", "Green")
                    ) +
  theme_classic() +
  ylim(0, 100) +
  theme(axis.ticks = element_blank(), axis.text.x = element_blank()) +
  labs(x="Container", y="Mean Probability")

data_plot

d.stats$container<-factor(d.stats$container, labels = c("Blue","Red","Purple","Green"))
d.stats$cond<-factor(d.stats$cond, labels = c("Ignorance", "Knowledge-implausible", "Knowledge-plausible"))

#Graph in report
ggplot(data = d.stats, 
                   aes(x = container, y = avg_resp, fill = cond)) + 
  geom_bar(stat = "identity", width=0.7, position=position_dodge(0.7))+  
  geom_errorbar(position=position_dodge(0.7), width = 0.1,
                aes(ymin = avg_resp - ci95, ymax = avg_resp + ci95)) +
  scale_fill_brewer(type='qual',palette=1) +
  theme_classic() +
  ylim(0, 100 ) +
  labs(x="Container", y="Mean Probability")+
  guides(fill=guide_legend("Condition"))


#ORIGINAL DATA

#Load and organize original data
d.orig = read.csv("BB_origData.csv")
d.orig$container <- ordered(d.orig$container, levels=c("blue", "red", "purple", "green"), labels=c("Blue", "Red", "Purple", "Green"))

d.orig$sterr = d.orig$sd / sqrt(d.orig$n)
d.orig$ci95 = d.orig$sterr*1.96

#Alternative graph
data_Origplot = ggplot(data = d.orig, aes(x = container, y = avg_resp, fill = container)) + 
  geom_bar(stat = "identity") + facet_wrap(~cond) + 
  geom_errorbar(width = .1, aes(ymin = avg_resp - ci95, ymax = avg_resp + ci95)) +
  scale_fill_manual(values=c("#0066CC", "#FF3333", "#990099", "#669933"),
                      labels=c("Blue", "Red", "Purple", "Green")) +
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
  ylim(0, 100) +
  labs(x="Container", y="Mean Probability")

data_Origplot

d.orig$cond<-factor(d.orig$cond, labels = c("Ignorance", "Knowledge-implausible", "Knowledge-plausible"))

#Graph in report
ggplot(data = d.orig, 
                   aes(x = container, y = avg_resp, fill = cond)) + 
  geom_bar(stat = "identity", width=0.7, position=position_dodge(0.7))+  
  geom_errorbar(position=position_dodge(0.7), width = 0.1,
                aes(ymin = avg_resp - ci95, ymax = avg_resp + ci95)) +
  scale_fill_brewer(type='qual',palette=1)+
  theme_classic() +
  ylim(0, 100 ) +
  labs(x="Container", y="Mean Probability") +
  guides(fill=guide_legend("Condition"))

```

#Stats from Birch and Bloom

``` {r BB_stats}

#Subset data by condition

#Ignorance condition
d.another = filter(d.wide, cond=="another")

#Know-plausible
d.red = filter(d.wide, cond=="the red")

#Know-implausible
d.purple = filter(d.wide, cond=="the purple")

#Compare red container: ignorance v. know-plausible

t.IgKp.red = t.test(d.another$red_norm, d.red$red_norm, alternative = "two.sided", paired = FALSE); t.IgKp.red
#t = -1.2029, df = 149.579, p-value = 0.2309

#Compare blue container: ignorance v. know-plausible

t.IgKp.blue = t.test(d.another$blue_norm, d.red$blue_norm, alternative = "two.sided", paired = FALSE); t.IgKp.blue
#t = -0.5202, df = 128.554, p-value = 0.6038

#Compare purple container: ignorance v. know-implausible

t.IgKImp.purp = t.test(d.another$purple_norm, d.purple$purple_norm, alternative = "two.sided", paired = FALSE); t.IgKImp.purp
#t = 0.3642, df = 133.889, p-value = 0.7163

#Compare blue container: ignorance v. know-implausible

t.IgKImp.blue = t.test(d.another$blue_norm, d.purple$blue_norm, alternative = "two.sided", paired = FALSE); t.IgKImp.blue
#t = -1.2719, df = 128.666, p-value = 0.2057

#Compare blue container: know-plausible v. know-implausible
t.KpKImp.blue = t.test(d.red$blue_norm, d.purple$blue_norm, alternative = "two.sided", paired = FALSE); t.KpKImp.blue
#t = -0.8818, df = 153.516, p-value = 0.3793

#Compare the purple and red containers: know-plausible v. know-implausible
t.KpKImp.purpred = t.test(d.red$red_norm, d.purple$purple_norm, alternative = "two.sided", paired = FALSE); t.KpKImp.purpred
#t = 5.106, df = 147.936, p-value = 9.975e-07


#Mixed model
library(lme4)

d.noGreen = filter(d.tidy, container != "green_norm")

d.noGreen$container = factor(d.noGreen$container)

#Orthogonal contrasts comparing blue and red containers
contrasts(d.noGreen$container) <- matrix(c(1,-1,0, 1,1,-2), nrow=3, byrow=FALSE)
contrasts(d.noGreen$container)

contrasts(d.noGreen$cond)
d.mixMod = lmer(response_norm ~ cond * container + (1 | workerid), d.noGreen)
summary(d.mixMod)

#Orthogonal contrasts comparing blue and purple containers
contrasts(d.noGreen$container) <- matrix(c(1,0,-1, 1,-2,1), nrow=3, byrow=FALSE)
contrasts(d.noGreen$container)

d.mixMod2 = lmer(response_norm ~ cond * container + (1 | workerid), d.noGreen)
summary(d.mixMod2)

```

``` {r}

#Exploratory Analyses

#Compare purple container: know-plausible v. know-implausible
t.KpKImp.purp = t.test(d.red$purple_norm, d.purple$purple_norm, alternative = "two.sided", paired = FALSE); t.KpKImp.purp
#t = -1.3429, df = 133.149, p-value = 0.1816

#Compare red container: know-plausible v. know-implausible
t.KpKImp.red = t.test(d.red$red_norm, d.purple$red_norm, alternative = "two.sided", paired = FALSE); t.KpKImp.red
#t = 1.9449, df = 157.986, p-value = 0.05356

```

```{r subject_data}

#Restructuring and reviewing demographic 
sub.data$colorblind = factor(sub.data$colorblind)
sub.data$gender = factor(sub.data$gender)
sub.data$education = factor(sub.data$education)
sub.data$age = as.numeric(sub.data$age)
sub.data$asses = factor(sub.data$asses)

age_sd = sd(sub.data$age, na.rm = TRUE); age_sd
age_mean = mean(sub.data$age, na.rm = TRUE); age_mean

```
